Spectral Variability of Two Rapidly Rotating Brown Dwarfs: \\2MASS~J08354256$-$0819237 and 2MASS~J18212815+1414010

### 2017-01-27 ms.tex
I added a new amplitude spectrum for 2MASS 0835 this time where I let A be +/- and impose a prior on the rotation period.

\begin{figure*}[!t]
\centering
\subfloat[2MASS J1821 - 2.5$\times \sigma$]{
	\includegraphics[width=0.5\textwidth]{2mass_1821_spectrum_0250perc_err_taurestrict.pdf}
	\label{fig:ampSpec0835times2p5ErrTauRest}
	}
\subfloat[2MASS J1821 - 4$\times \sigma$ ]{
	\includegraphics[width=0.5\textwidth]{2mass_1821_spectrum_0400perc_err_taurestrict.pdf}
	\label{fig:ampSpec1821fourTimesErr}
	}
	\caption{Restricting the $\tau$ parameter to, $3.8 < \tau < 4.0$ significantly reduces the long term quadratic terms' contribution to the sinusoidal fit. In this case, there were MCMC fits for \shb, one with error bars scaled by 2.5$\sigma$ and the other by 4.0$\sigma$.}
	\label{fig:ampSpecManualSTauRestrict}
	\vspace{0.1in}
\end{figure*}

>>>>

\begin{figure*}[!t]
\centering
\subfloat[2MASS J1821 - 2.5$\times \sigma$]{
	\includegraphics[width=0.5\textwidth]{2mass_0835_spectrum_0250perc_err_taurestric.pdf}
	\label{fig:ampSpec0835times2p5ErrTauRest}
	}
\subfloat[2MASS J1821 - 4$\times \sigma$ ]{
	\includegraphics[width=0.5\textwidth]{2mass_1821_spectrum_0400perc_err_taurestrict.pdf}
	\label{fig:ampSpec1821fourTimesErr}
	}
	\caption{Restricting the $\tau$ parameter to, $3.8 < \tau < 4.0$ significantly reduces the long term quadratic terms' contribution to the sinusoidal fit. In this case, there were MCMC fits for \shb, one with error bars scaled by 2.5$\sigma$ and the other by 4.0$\sigma$.}
	\label{fig:ampSpecManualSTauRestrict}
	\vspace{0.1in}
\end{figure*}

As with \shb\ I imposed a tight prior on $\tau$ such that $3.0 < \tau < 3.2$ for \sha. This now gives an average amplitude of zero -- see Figure \ref{fig:amp2mass08352p5ErrTauRest}.

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{2mass_0835_spectrum_0250perc_err_taurestric.pdf}
\caption{Amplitude spectrum for \sha\ with error bars scaled by 2.5$\sigma$. The average amplitude is zero.}\label{fig:amp2mass08352p5ErrTauRest}
\end{centering}
\end{figure}
